---
title: 'Tutorial 8: Table 4'
author: "Wei-Chun Chou"
advisor: "Zhoumeng Lin"
date: "June, 2020"
fontsize: 12pt
output:
  html_document:
    theme: cerulean 
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## knitr::opts_knit$set(root.dir = set up the direction file where your "PlotCode" file is)
knitr::opts_knit$set(root.dir = "C:/Users/weichunc/Dropbox/PostDoc_KSU/Project/Project 1- PFOX PBPK/PART IV-Pregnacy PBPK mdoel/Sumission_EHP/R2+Revision_EHP/Additional files/Results/PlotCode")
```

# Introduction
This tutorial aims to guide you to step-by-step reproduce the results of Table 4: Model predicted and measured concentrations of PFOS in maternal plasma, maternal liver, fetal/neonatal plasma and fetal/neonatal liver at the end of gestation (GD21), early (PND5) and later lactation (PND21) periods 

# Prerequisites
Before running your model, you should set up your working directory, compile the PBPK model, install all required packages and input needed datasets. The model file and datasets can be found in the additional files. 
## Setting up your working directory
The working directory has to be changed to the **PlotCode** folder. You can use two ways to change your working directory as follow:

1. Use RStudio: use the menu to change your working directory under **Session > Set Working Directory > Choose Directory**. <br>
2. Use R function: use the R function `setwd()` to change the path to your working directory.  

## Loading required R packages  
The list of R packages should be installed prior to the simulation. If you have not installed these packages (listed below), please install these packages to your Rstudio using the R function `require (" ")` and then use `library` open it.

```{r package, echo=TRUE, message=FALSE}
##  Loading requried R packages
library(mrgsolve)    ## R-package for Loading mrgsolve code 
library(magrittr)    ## R-package for the pipe, %>% , c
library(dplyr)       ## R-package for transform and summarize 
library(tidyverse)   ## R-package for transform and summarize 
library(ggplot2)     ## R-package for GGplot
library(FME)         ## R-package for model fitting
library(minpack.lm)  ## R-package for model fitting
library(ggExtra)     ## R-package for function "grid.arrange" 
library(EnvStats)    ## R-package for function "rlnormTrunc"
```

## Read mrgsolve-based PBPK Model R file
The pre-pregnant, gestational and lactational PBPK models in humans were written in `HMod.R` file. Before compiling the model, please conduct/call this file using R function `source`. 

```{r Input}
## Input mrgsolve-based PBPK Model
source (file = "RMod.R")

```

## Complie mrgsolve-based PBPK Model
Read the code and build these mrgsolve-based PBPK models. You should make sure all models are built correctly. 

```{r}
## Build mrgsolve-based PBPK Model
PreGmod_R <- mcode ("PreG_RatPBPK.code", PreG_RatPBPK.code)
Gmod_R    <- mcode ("GRatPBPK.code", GRatPBPK.code)
Lmod_R    <- mcode ("LRatPBPK.code", LRatPBPK.code)
```

## Loading datasets
In this step, you need to input the .csv file to the Rstudio. The function `read.csv` can be used to read the csv files into R

```{r}
RDat <- read.csv(file = "Data_R.csv") 

```

## Loading Fit results from rds files to obtain final parameter values
```{r}
GFit_R <- readRDS(file = "GFit_R.rds")
LFit_R <- readRDS(file = "LFit_R.rds")
```

## Input prediction function
```{r}
source (file = "Pred_Rat.R")
```

# Define prediction function
The prediction function is defined to simulate the time-vayring profiles of PFOS in maternal plasma, liver, fetal/neonatal plasma and liver during gestation and lactation.

```{r}
## Define the prediction function
pred.C <- function(Gpars, Lpars, DOSE) {
    
PreG_BW          = 0.20 ## Female rat body weight (premating); 
tinterval        = 24   ## Time interval; 
PreG_TDOSE       = 42 + 14  ## Total dosing/Dose times; Repeat oral dose from beginning 42 days prior to cohabitation; (14 days mating)
PreG_DOSE        = DOSE ## Repeat oral dose (mg/kg/day);  
PreG_DOSEoral    = PreG_DOSE*PreG_BW ## Amount of oral dose
    
    
# To create a data set of 1 subject receiving DOSEoral.A every 24 hours
PreG_ex.oral <- ev (ID   = 1,             ## One individual
                    amt  = PreG_DOSEoral, ## Amount of dose 
                    ii   = tinterval,     ## Time interval
                    addl = PreG_TDOSE - 1,## Additional doseing 
                    cmt  = "AST", ## The dosing compartment: AST Stomach  
                    replicate = FALSE)    ## No replicate
    
## Simulation time from 6 weeks prior to mating througout 14 days of mating period
PreG_tsamp = tgrid(0, tinterval*(PreG_TDOSE - 1) + 24*1, 1) 

PreG_out <- PreGmod_R %>% 
update(atol = 1E-6, maxsteps = 500000) %>%          
mrgsim_d (data = PreG_ex.oral, tgrid = PreG_tsamp)
    
PreG_Init <- PreG_out %>% filter (time == (56*24)) %>% select(-c("Plasma", "Liver","Kidney"))
    
############### Gestational model
## Get out of log domain
Gpars <- exp(Gpars) ## Return a list of exp (parameters) 
    
## Exposure scenario for gestational exposure
GBW          = 0.36                   ## Body weight during gestation from Luebker et al., 2005b
tinterval = 24  ## Time interval; 
GTDOSE = 22  ## Total dosing/Dose times; Repeat oral dose from GD0 - GD21
GDOSE        = DOSE                   ## Repeat oral dose 
GDOSEoral    = GDOSE*GBW              ## Amount of oral dose
    
# To create a data set of 1 subject receiving DOSE every 24 hours 
Gex.oral <- ev (ID   = 1,             ## One individual
            amt  = GDOSEoral,     ## Amount of dose 
            ii   = tinterval,     ## Time interval
            addl = GTDOSE - 1,    ## Additional doseing 
            cmt  = "AST",         ## The dosing compartment: AST Stomach  
            tinf = 0.01,          ## Infusion time;  
            replicate = FALSE)    ## No replicate
    
Gtsamp  = tgrid(0, tinterval*(GTDOSE - 1) + 24*1, 1) ## Exposure time from GD0 to GD21 and plus 1 day without dosing
    
## Simulation: 
## Gout_1 based on the dosing regimen of Luebker et al., 2005ab

Gout_1 <- 
Gmod_R %>%
init(APlas_free = PreG_Init$APlas_free, APTC = PreG_Init$APTC, AFil = PreG_Init$AFil, AKb = PreG_Init$AKb, ARest = PreG_Init$ARest,
AL = PreG_Init$AL, AM = PreG_Init$AM, AF = PreG_Init$AF, A_baso = PreG_Init$A_baso, A_apical = PreG_Init$A_apical, Adif = PreG_Init$Adif,
Aefflux = PreG_Init$Aefflux) %>%
param (Gpars) %>%
update(atol = 1E-6, maxsteps = 500000) %>%          
mrgsim_d (data = Gex.oral, tgrid = Gtsamp)

## Gout_2 based on the dosing regimen of Chang et al., 2009
Gout_2 <- 
Gmod_R %>%
param (Gpars) %>%
update(atol = 1E-6, maxsteps = 500000) %>%          
mrgsim_d (data = Gex.oral, tgrid = Gtsamp)
    
Goutdf_1 = cbind.data.frame(
           Time      = Gout_1$time, 
           CPlas     = Gout_1$Plasma,
           CL        = Gout_1$Liver,
           CPlas_pup = Gout_1$Plasma_Fet,
                              CL_pup    = Gout_1$Liver_Fet) 
    
Goutdf_2 = cbind.data.frame(Time      = Gout_2$time, 
                                CPlas     = Gout_2$Plasma,
                                CL        = Gout_2$Liver,
                                CPlas_pup = Gout_2$Plasma_Fet,
                                CL_pup    = Gout_2$Liver_Fet)
    
    GInit <- Gout_1 %>% filter (time == 21*24) 
    
### Lactational model 
Lpars <- exp(Lpars) ## Return a list of exp (parametrs) 
## Exposure scenario for lactational exposure; through PND0 - PND21 (end of lactation)
LBW          = 0.26  ## Rat body weight during lactation from Luebker et al., 2005b
tinterval    = 24    ## Time interval; 
LTDOSE       = 23    ## Total dosing/Dose times;  PND0 - PND22
LDOSE        = DOSE  ## Repeat oral dose of GDOSE mg/kg/day;  
LDOSEoral    = LDOSE*LBW  ## Amount of oral dose
    
# To create a data set of 1 subject receiving DOSEoral.A every 24 hours
Lex.oral <- ev (ID   = 1,            ## One individual
            amt  = LDOSEoral,    ## Amount of dose 
            ii   = tinterval,    ## Time interval
            addl = LTDOSE - 1,   ## Additional doseing 
            cmt  = "AST",        ## The dosing compartment: AST Stomach  
            tinf = 0.01,          ## Infusion time;  
            replicate = FALSE)   ## No replicate
    
Ltsamp       = tgrid(0, tinterval*(LTDOSE - 1) + 24*2, 1) ## Simulation time from PND0 to PND22 plus 2 days without dosing
    
    
Lout <- Lmod_R %>% 
init(APlas_free = GInit$APlas_free, APTC = GInit$APTC, AFil = GInit$AFil, AKb = GInit$AKb, ARest = GInit$ARest,
AL = GInit$AL, AM = GInit$AM, AF = GInit$AF, A_baso = GInit$A_baso, A_apical = GInit$A_apical, Adif = GInit$Adif,
Aefflux = GInit$Aefflux, APlas_free_pup = GInit$APlas_Fet_free, 
ARest_pup = GInit$ARest_Fet, AL_pup  = GInit$AL_Fet) %>%
param (Lpars) %>%
update(atol = 1E-6, maxsteps = 500000) %>%          
mrgsim_d (data = Lex.oral, tgrid = Ltsamp)
    
Loutdf = cbind.data.frame(Time   = Lout$time, 
                          CPlas  = Lout$Plasma, 
                          CL     = Lout$Liver, 
                          CPlas_pup = Lout$Plasma_pup,
                          CL_pup = Lout$Liver_pup)
    
return (list(Goutdf_1, Loutdf, Goutdf_2))
}
```

# Monte Carlo Simulation
In the Monte Carlo Simulation, the sensitive parameters were chosen by sensitivity analysis and then were assigned as probabilistic distributions (please refer to Table S8-S9). 

```{r}
# create several empty list ()
## Following dosing 0.1 mg/kg/day during gestaion and lactation
outdf_0.1_G <- list()
outdf_0.1_L <- list()
outdf_0.1_G2 <- list()

## Following dosing 0.3 mg/kg/day during gestaion and lactation
outdf_0.3_G <- list()
outdf_0.3_L <- list()
outdf_0.3_G2 <- list()

## Following dosing 0.4 mg/kg/day during gestaion and lactation
outdf_0.4_G <- list()
outdf_0.4_L <- list()
outdf_0.4_G2 <- list()

## Following dosing 1 mg/kg/day during gestaion and lactation
outdf_1.0_G <- list()
outdf_1.0_L <- list()
outdf_1.0_G2 <- list()

## Following dosing 1.6 mg/kg/day during gestaion and lactation
outdf_1.6_G <- list()
outdf_1.6_L <- list()
outdf_1.6_G2 <- list()

## Following dosing 3.2 mg/kg/day during gestaion and lactation
outdf_3.2_G <- list()
outdf_3.2_L <- list()
outdf_3.2_G2 <- list()


## Monte carlo simulation 
N = 10 # 1000
for (i in 1:N) {
    pars_G  <- log(c(
        BW        = rnormTrunc (1, min = 0.15, max = 0.57, mean = 0.36, sd = 0.108),
        VLC       = rnormTrunc  (1, min = 0.01, max = 0.06, mean = 0.04, sd = 0.01),
        KbileC    = rlnormTrunc (1, min = exp(-5.38), max = exp(-4.63), meanlog = -5.00, sdlog = 0.19),
        PL        = rlnormTrunc (1, min = exp(0.88), max = exp(1.39), meanlog = 1.13, sdlog = 0.13),
        PRest     = rlnormTrunc (1, min = exp(-1.79), max = exp(-1.28), meanlog = -1.53, sdlog = 0.13),
        Ktrans1C  = rlnormTrunc (1, min = exp(-0.18), max = exp(0.58), meanlog = 0.20, sdlog = 0.19),
        Ktrans2C  = rlnormTrunc (1, min = exp(-0.42), max = exp(0.34), meanlog = -0.04, sdlog = 0.19),
        Ktrans3C  = 0.23,
        Free      = 0.019,
        Vmax_baso_invitro = 221,
        Km_baso   = 19.9,
        Free_Fet  = 0.022,
        PL_Fet    = 2.55
    ))    
    
    pars_L  <- log(c(
        Free        = rlnormTrunc (1, min = exp(-6.01), max = exp(-5.32), meanlog = -5.62, sdlog = 0.198),
        Free_pup    = rlnormTrunc (1, min = exp(-4.22), max = exp(-3.44), meanlog = -3.84, sdlog = 0.198),
        GFRC        = rnormTrunc  (1, min = 24.95, max = 57.13, mean = 41, sd = 8.208),
        KbileC      = rlnormTrunc (1, min = exp(-6.57), max = exp(-5.41), meanlog = -5.99, sdlog = 0.294),
        Km_apical_p = rlnormTrunc (1, min = exp(5.009), max = exp(6.16), meanlog = 5.58, sdlog = 0.29),
        KMilk0      = rlnormTrunc (1, min = exp(-1.68), max = exp(-0.90), meanlog = -1.29, sdlog = 0.13), 
        KurineC_pup = rlnormTrunc (1, min = exp(-0.148), max = exp(1.002), meanlog = 0.45, sdlog = 0.19),
        PL          = rlnormTrunc (1, min = exp(0.59), max = exp(1.37), meanlog = 0.98, sdlog = 0.198),
        PL_pup      = rlnormTrunc (1, min = exp(0.53), max = exp(1.30), meanlog = 0.92, sdlog = 0.198),
        PMilkM      = rlnormTrunc (1, min = exp(0.22), max = exp(1.17), meanlog = 0.60, sdlog = 0.19),
        PRest_pup   = rlnormTrunc (1, min = exp(-1.92), max = exp(-1.14), meanlog = -1.53, sdlog = 0.13),
        RAFapi      = rlnormTrunc (1, min = exp(0.80), max = exp(1.955), meanlog = 1.38, sdlog = 0.29),
        VFilC       = rnormTrunc  (1, min = 0.00035, max = 0.00133, mean = 0.00084, sd = 0.00025),
        Vmax_apical_invitro_p = rlnormTrunc (1, min = exp(5.35), max = exp(6.507), meanlog = 5.93, sdlog = 0.29),
        Vmax_apical_invitro = 4141,
        PRest       = 0.03,
        SA_BW       = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_VLC      = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_KMilkC   = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_VL_pup   = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2) 
    ))

## Save the prediction results to the list () and label the dose group
## 0.1 dose group list
outdf_0.1_G [[i]] <- pred.C(pars_G, pars_L, 0.1)[[1]] %>% 
    mutate(ID = i, Dose_group = 0.1)
outdf_0.1_L [[i]] <- pred.C(pars_G, pars_L, 0.1)[[2]] %>% 
    mutate(ID = i, Dose_group = 0.1)
outdf_0.1_G2 [[i]] <- pred.C(pars_G, pars_L, 0.1)[[3]] %>% 
    mutate(ID = i, Dose_group = 0.1)

## 0.3 dose group list
outdf_0.3_G [[i]] <- pred.C(pars_G, pars_L, 0.3)[[1]] %>% 
    mutate(ID = i, Dose_group = 0.3)
outdf_0.3_L [[i]] <- pred.C(pars_G, pars_L, 0.3)[[2]] %>% 
    mutate(ID = i, Dose_group = 0.3)
outdf_0.3_G2 [[i]] <- pred.C(pars_G, pars_L, 0.3)[[3]] %>% 
    mutate(ID = i, Dose_group = 0.3)

## 0.4 dose group list
outdf_0.4_G [[i]] <- pred.C(pars_G, pars_L, 0.4)[[1]] %>% 
    mutate(ID = i, Dose_group = 0.4)
outdf_0.4_L [[i]] <- pred.C(pars_G, pars_L, 0.4)[[2]] %>% 
    mutate(ID = i, Dose_group = 0.4)
outdf_0.4_G2 [[i]] <- pred.C(pars_G, pars_L, 0.4)[[3]] %>% 
    mutate(ID = i, Dose_group = 0.4)

## 1.0 dose group list
outdf_1.0_G [[i]] <- pred.C(pars_G, pars_L, 1)[[1]] %>% 
    mutate(ID = i, Dose_group = 1)
outdf_1.0_L [[i]] <- pred.C(pars_G, pars_L, 1)[[2]] %>% 
    mutate(ID = i, Dose_group = 1)
outdf_1.0_G2 [[i]] <- pred.C(pars_G, pars_L, 1)[[3]] %>% 
    mutate(ID = i, Dose_group = 1)

## 1.6 dose group list
outdf_1.6_G [[i]] <- pred.C(pars_G, pars_L, 1.6)[[1]] %>% 
    mutate(ID = i, Dose_group = 1.6)
outdf_1.6_L [[i]] <- pred.C(pars_G, pars_L, 1.6)[[2]] %>% 
    mutate(ID = i, Dose_group = 1.6)
outdf_1.6_G2 [[i]] <- pred.C(pars_G, pars_L, 1.6)[[3]] %>% 
    mutate(ID = i, Dose_group = 1.6)

## 3.2 dose group list
outdf_3.2_G [[i]] <- pred.C(pars_G, pars_L, 3.2)[[1]] %>% 
    mutate(ID = i, Dose_group = 3.2)
outdf_3.2_L [[i]] <- pred.C(pars_G, pars_L, 3.2)[[2]] %>% 
    mutate(ID = i, Dose_group = 3.2)
outdf_3.2_G2 [[i]] <- pred.C(pars_G, pars_L, 3.2)[[3]] %>% 
    mutate(ID = i, Dose_group = 3.2)
    
}
```

# Summary mean and SD in each dose group
```{r}
## The range of 0.1 mg/kg/day dose group
Range_0.1_GD20 <- do.call (rbind, outdf_0.1_G2)%>% 
    filter (Time == 20*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.1_GD21 <- do.call (rbind, outdf_0.1_G)%>% 
    filter (Time == 21*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.1_PND5 <- do.call (rbind, outdf_0.1_L)%>% 
    filter (Time == 24*5) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.1_PND21 <- do.call (rbind, outdf_0.1_L)%>% 
    filter (Time == 24*21) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

## The range of 0.3 mg/kg/day dose group
Range_0.3_GD20 <- do.call (rbind, outdf_0.3_G2)%>% 
    filter (Time == 20*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.3_GD21 <- do.call (rbind, outdf_0.3_G)%>% 
    filter (Time == 21*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.3_PND5 <- do.call (rbind, outdf_0.3_L)%>% 
    filter (Time == 24*5) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.3_PND21 <- do.call (rbind, outdf_0.3_L)%>% 
    filter (Time == 24*21) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))


## The range of 0.4 mg/kg/day dose group
Range_0.4_GD20 <- do.call (rbind, outdf_0.4_G2)%>% 
    filter (Time == 20*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.4_GD21 <- do.call (rbind, outdf_0.4_G)%>% 
    filter (Time == 21*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.4_PND5 <- do.call (rbind, outdf_0.4_L)%>% 
    filter (Time == 24*5) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_0.4_PND21 <- do.call (rbind, outdf_0.4_L)%>% 
    filter (Time == 24*21) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

## The range of 1 mg/kg/day dose group
Range_1.0_GD20 <- do.call (rbind, outdf_1.0_G2)%>% 
    filter (Time == 24*20) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_1.0_GD21 <- do.call (rbind, outdf_1.0_G)%>% 
    filter (Time == 24*21) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_1.0_PND5 <- do.call (rbind, outdf_1.0_L)%>% 
    filter (Time == 5*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_1.0_PND21 <- do.call (rbind, outdf_1.0_L)%>% 
    filter (Time == 21*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

## The range of 1.6 mg/kg/day dose group
Range_1.6_GD20 <- do.call (rbind, outdf_1.6_G2)%>% 
    filter (Time == 20*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_1.6_GD21 <- do.call (rbind, outdf_1.6_G)%>% 
    filter (Time == 24*21) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_1.6_PND5 <- do.call (rbind, outdf_1.6_L)%>% 
    filter (Time == 5*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_1.6_PND21 <- do.call (rbind, outdf_1.6_L)%>% 
    filter (Time == 21*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))


## The range of 3.2 mg/kg/day dose group
Range_3.2_GD20 <- do.call (rbind, outdf_3.2_G2)%>% 
    filter (Time == 20*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))


Range_3.2_GD21 <- do.call (rbind, outdf_3.2_G)%>% 
    filter (Time == 21*24) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))


Range_3.2_PND5 <- do.call (rbind, outdf_3.2_L)%>% 
    filter (Time == 5*24 & CPlas_pup < 1000 & CL_pup < 1000) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

Range_3.2_PND21 <- do.call (rbind, outdf_3.2_L)%>% 
    filter (Time == 21*24& CPlas_pup < 1000 & CL_pup < 1000) %>% 
    summarize (
    Mean_CPlas      = mean(CPlas), 
    SD_CPlas        = sd (CPlas), 
    Mean_CPlas_pup  = mean(CPlas_pup), 
    SD_CPlas_pup    = sd (CPlas_pup),
    Mean_CL         = mean(CL), 
    SD_CL           = sd(CL),
    Mean_CL_pup     = mean(CL_pup), 
    SD_CL_pup       = sd(CL_pup))

```

# Show the predicted values
Here, we make a table to display the predicted mean and SD in maternal plasma (CPlas) and liver (CL), and fetal/neonatal plasma (CPlas_pup) and liver (CL_pup) following dosing of 0.1, 0.3, 0.4, 1, 1.6 and 3.2 on gestational day (GD)20, GD21, postnatal day(PND)5 and PND21. These time points were selected based on available data.

```{r}
# The mean and SD on the 0.1 dose group on GD20, GD21, PND5 and PND21
Range_0.1 = rbind.data.frame(
            GD20  = Range_0.1_GD20,
            GD21  = Range_0.1_GD21,
            PND5  = Range_0.1_PND5,
            PND21 = Range_0.1_PND21)

Range_0.1  
# The mean and SD on the 0.3 dose group on GD20, GD21, PND5 and PND21
Range_0.3 = rbind.data.frame(
            GD20  = Range_0.3_GD20,
            GD21  = Range_0.3_GD21,
            PND5  = Range_0.3_PND5,
            PND21 = Range_0.3_PND21)

Range_0.3  
# The mean and SD on the 0.4 dose group on GD20, GD21, PND5 and PND21
Range_0.4 = rbind.data.frame(
            GD20  = Range_0.4_GD20,
            GD21  = Range_0.4_GD21,
            PND5  = Range_0.4_PND5,
            PND21 = Range_0.4_PND21)

Range_0.4
# The mean and SD on the 1 dose group on GD20, GD21, PND5 and PND21
Range_1.0 = rbind.data.frame(
            GD20  = Range_1.0_GD20,
            GD21  = Range_1.0_GD21,
            PND5  = Range_1.0_PND5,
            PND21 = Range_1.0_PND21)

Range_1.0

# The mean and SD on the 1.6 dose group on GD20, GD21, PND5 and PND21
Range_1.6 = rbind.data.frame(
            GD20  = Range_1.6_GD20,
            GD21  = Range_1.6_GD21,
            PND5  = Range_1.6_PND5,
            PND21 = Range_1.6_PND21)

Range_1.6

# The mean and SD on the 3.2 dose group on GD20, GD21, PND5 and PND21
Range_3.2 = rbind.data.frame(
            GD20  = Range_3.2_GD20,
            GD21  = Range_3.2_GD21,
            PND5  = Range_3.2_PND5,
            PND21 = Range_3.2_PND21)

Range_3.2

```


