---
title: 'Tutorial 9: Table 5'
author: "Wei-Chun Chou"
advisor: "Zhoumeng Lin"
dae: "June, 2020"
fonttsize: 12pt
output:
  html_document:
    theme: cerulean 
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## knitr::opts_knit$set(root.dir = set up the direction file where your "PlotCode" file is)
knitr::opts_knit$set(root.dir = "C:/Users/weichunc/Dropbox/PostDoc_KSU/Project/Project 1- PFOX PBPK/PART IV-Pregnacy PBPK mdoel/Sumission_EHP/R2+Revision_EHP/Additional files/Results/PlotCode")
```

# Introduction
This tutorial aims to guide you to step-by-step reproduce the results of Table 5: Comparison of the derived average serum concentration (ASC) and human equivalent dose (HED) from the rat and human models with the values from U.S. EPA guidance 

# Prerequisites
Before running your model, you should set up your working directory, compile the PBPK model, install all required packages and input needed datasets. The model file and datasets can be found in the additional files. 

## Setting up your working directory
The working directory has to be changed to the **PlotCode** folder. You can use two ways to change your working directory as follow:

1. Use RStudio: use the menu to change your working directory under **Session > Set Working Directory > Choose Directory**. <br>
2. Use R function: use the R function `setwd()` to change the path to your working directory.  

## Loading required R packages  
The list of R packages should be installed prior to the simulation. If you have not installed these packages (listed below), please install these packages to your Rstudio using the R function `require (" ")` and then use `library` open it.

```{r package, echo=TRUE, message=FALSE}
##  Loading requried R packages
library(mrgsolve)    ## R-package for Loading mrgsolve code 
library(magrittr)    ## R-package for the pipe, %>% , c
library(dplyr)       ## R-package for transform and summarize 
library(tidyverse)   ## R-package for transform and summarize 
library(ggplot2)     ## R-package for GGplot
library(FME)         ## R-package for model fitting
library(minpack.lm)  ## R-package for model fitting
library(ggExtra)     ## R-package for function "grid.arrange" 
library(EnvStats)    ## R-package for function "rlnormTrunc"
```

## Read mrgsolve-based PBPK Model R file
The pre-pregnant, gestational and lactational PBPK models in humans were written in `HMod.R` file. Before compiling the model, please conduct/call this file using R function `source`. 

```{r Input}
## Input mrgsolve-based PBPK Model
source (file = "RMod.R")
source (file = "HMod.R")

```

## Compile mrgsolve-based PBPK Model
Read the code and build these mrgsolve-based PBPK model. You should make sure all models are built correctly. 

```{r}
## Build mrgsolve-based PBPK Model
PreGmod_R <- mcode ("PreG_RatPBPK.code", PreG_RatPBPK.code)
Gmod_R    <- mcode ("GRatPBPK.code", GRatPBPK.code)
Lmod_R    <- mcode ("LRatPBPK.code", LRatPBPK.code)

PreGmod_H <- mcode ("PreGHumanPBPK.code", PreGHumanPBPK.code) 
Gmod_H    <- mcode ("GHumanPBPK.code", GHumanPBPK.code)
Lmod_H    <- mcode ("LHumanPBPK.code", LHumanPBPK.code)

```

## Loading datasets
In this step, you need to input the .csv file to the Rstudio. The function `read.csv` can be used to read the csv files into R

```{r}
RDat <- read.csv(file = "Data_R.csv") 
HDat <- read.csv(file = "Data_H.csv")

```

## Loading Fit results from rds files to obtain the final parameter values
```{r}
GFit_R <- readRDS(file = "GFit_R.rds")
LFit_R <- readRDS(file = "LFit_R.rds")
GFit_H <- readRDS(file = "GFit_H.rds")
LFit_H <- readRDS(file = "LFit_H.rds")
```

## Input prediction function
```{r}
source (file = "Pred_Rat.R")
source (file = "Pred_H.R")
```

# Define the prediction function
Here, we define rat and human prediction functions to predict the maternal plasma AUC through gestation to lactation period.<br>

In the rat prediction function `pred.rat`, we follow the study designs of selected animal studies to develop the perdiction function:

1. Luebker et al. 2005a: the NOAEL of 0.1 mg/kg/day was derived from a rat study following the dosing through prior matting (42 days prior mating and 14 days during mating), gestation (GD0-GD22) and lactation (PND0-PND20).  

2. Luebker et al. 2005b: the NOAEL of 0.4 mg/kg/day was derived from a rat study following the dosing through prior matting (42 days prior mating and 14 days during mating) and gestation (22 days from GD0 to GD21).

3. Butenhoff et al. 2009: the NOALE of 0.3 mg/kg/day was derived from a rat study following the dosing through gestation (21 days) to lactation (20 days).

4. Lau et al. 2003: the NOAEL of 1 mg/kg/day was derived from a rat study following dosing from GD2 to GD20.

In the human prediction function `pred.human`, we follow the exposure scenarios:

1. pre-pregnant preiod: People are daily exposed to PFOS via oral route from birth to 30 years old.
2. Gestaiton: the PFOS levels in the tissues predicted from pre-prengnat women are used as initial concentrations of the gestational model, and then the gestational model is simulated based on the scenario that prengnat women are daily exposed to PFOS from gestaitonal weeks (GA)0 to GA40. 
3. Lactation: the PFOS levels of tissues predicted from the gestational model are used as initial concentrations of the lactational model and then continue to simulate the PFOS exposure during lactation.

The maternal AUC predicted by the rat and human model is used to derive the human equivalent dose (HED) value (Please refer to the mnuscript).


```{r}
## Define prediction function based on the exposure scenario from literatures 
pred.rat <- function(Gpars_R, Lpars_R, DOSE) {
    
    ## Exposure scenario for Lactational exposure; through GD(-53) - GD21 (end of gestation)
    PreG_BW          = 0.25                         ## Rat body weight; 
    tinterval        = 24                           ## Time interval; 
    PreG_TDOSE       = 42 + 14                      ## Total dosing/Dose times; Repeat oral dose from beginning 42 days prior to cohabitation; (14 days matting)
    PreG_DOSE        = DOSE                         ## Repeat oral dose of GDOSE mg/kg/day;  
    PreG_DOSEoral    = PreG_DOSE*PreG_BW            ## Amount of oral dose
    
    
    # To create a data set of 1 subject receiving DOSEoral.A every 24 hours for 1 total doses
    PreG_ex.oral_R <- ev (ID   = 1,                 ## One individual
                          amt  = PreG_DOSEoral,     ## Amount of dose 
                          ii   = tinterval,         ## Time interval
                          addl = PreG_TDOSE - 1,    ## Addtional doseing 
                          cmt  = "AST",             ## The dosing comaprtment: AST Stomach  
                          replicate = FALSE)        ## No replicate
    
    PreG_tsamp_R       = tgrid(0, tinterval*(PreG_TDOSE - 1), 1) ## Simulation time from 6 weeks prior to mating and during mating (maximum of 14 days)
    
    PreG_out_R <- PreGmod_R %>% 
                  update(atol = 1E-8, maxsteps = 500000) %>%          
                  mrgsim_d (data = PreG_ex.oral_R, tgrid = PreG_tsamp_R)
    
    PreG_Init <- PreG_out_R %>% filter (row_number()== n()) %>% select(-c("Plasma", "Liver","Kidney"))
    
    ## Get out of log domain
    Gpars <- exp(Gpars_R)           ## Return a list of exp (parametrs for gestational model) from log scale

    
    ## Exposure scenario for gestational exposure
    GBW          = 0.3                    ## Body weight before gestation (measrument data if available); Default value adopted from Garner et al. (2015)
    tinterval    = 24                     ## Time interval; 
    GTDOSE       = 21                     ## Total dosing/Dose times; Repeat oral dose from GD0 - GD20
    GDOSE        = DOSE                   ## Repeat oral dose 
    GDOSEoral    = GDOSE*GBW              ## Amount of oral dose
    

    # To create a data set of 1 subject receiving DOSEoral every 24 hours 
    Gex.oral <- ev (ID   = 1,             ## One individual
                    amt  = GDOSEoral,     ## Amount of dose 
                    ii   = tinterval,     ## Time interval
                    addl = GTDOSE - 1,    ## Addtional doseing 
                    cmt  = "AST",         ## The dosing comaprtment: AST Stomach  
                    replicate = FALSE)    ## No replicate
    
    Gtsamp_A1  = tgrid(2, tinterval*(GTDOSE - 1) + 24*1, 1) ## Simulation time from GD2 to GD 21 
    Gtsamp_A2  = tgrid(0, tinterval*(GTDOSE - 1) + 24*1, 1) ## Simulation time from GD0 to GD 21 
    Gtsamp_A3  = tgrid(0, tinterval*(GTDOSE - 1) + 24*1, 1) ## Simulation time from GD0 to GD 21 
    Gtsamp_A4  = tgrid(0, tinterval*(GTDOSE - 1) + 24*1, 1) ## Simulation time from GD0 to GD 21 
    
    ## Simulation of exposure scenaior 
    Gout_A1 <- Gmod_R %>% param (Gpars) %>%
               update(atol = 1E-5, maxsteps = 500000) %>%          
               mrgsim_d (data = Gex.oral, tgrid = Gtsamp_A1)
    
    Gout_A2 <- Gmod_R %>% init(APlas_free = PreG_Init$APlas_free, APTC = PreG_Init$APTC, AFil = PreG_Init$AFil, AKb = PreG_Init$AKb, ARest = PreG_Init$ARest,
                               AL = PreG_Init$AL, AM = PreG_Init$AM, AF = PreG_Init$AF, A_baso = PreG_Init$A_baso, A_apical = PreG_Init$A_apical, Adif = PreG_Init$Adif,
                               Aefflux = PreG_Init$Aefflux) %>%
                               param (Gpars) %>% update(atol = 1E-5, maxsteps = 500000) %>%          
                               mrgsim_d (data = Gex.oral, tgrid = Gtsamp_A2)
    
    Gout_A3 <- Gmod_R %>% init(APlas_free = PreG_Init$APlas_free, APTC = PreG_Init$APTC, AFil = PreG_Init$AFil, AKb = PreG_Init$AKb, ARest = PreG_Init$ARest,
                               AL = PreG_Init$AL, AM = PreG_Init$AM, AF = PreG_Init$AF, A_baso = PreG_Init$A_baso, A_apical = PreG_Init$A_apical, Adif = PreG_Init$Adif,
                               Aefflux = PreG_Init$Aefflux) %>%
                               param (Gpars) %>% update(atol = 1E-5, maxsteps = 500000) %>%          
                               mrgsim_d (data = Gex.oral, tgrid = Gtsamp_A3)
    
    Gout_A4 <- Gmod_R %>% param (Gpars) %>%
               update(atol = 1E-5, maxsteps = 500000) %>%          
               mrgsim_d (data = Gex.oral, tgrid = Gtsamp_A4)
    

    Goutdf_A1 <- as.data.frame(Gout_A1) %>% select (Time = time, CPlas = Plasma, AUC_CPlas = AUC_CPlas)
    Goutdf_A2 <- as.data.frame(Gout_A2) %>% select (Time = time, CPlas = Plasma, AUC_CPlas = AUC_CPlas)
    Ginit_A3  <- as.data.frame(Gout_A3) %>% filter (row_number()== n()) 
    Ginit_A4  <- as.data.frame(Gout_A4) %>% filter (row_number()== n()) 
    
    ############### Lactational model ##############################
    Lpars <- exp(Lpars_R)          ## Return a list of exp (parametrs for gestational model) from log scale
    
    ## Exposure scenario for Lactational exposure; through PND0 - PND21 (end of lactation)
    LBW          = 0.35                  ## Rat body weight on PND0 (GD21); 
    tinterval    = 24                    ## Time interval; 
    LTDOSE       = 21                    ## Total dosing/Dose times; Repeat oral dose from PND0 - PND20
    LDOSE        = DOSE                  ## Repeat oral dose   
    LDOSEoral    = LDOSE*LBW             ## Amount of oral dose
    
    
    # To create a data set of 1 subject receiving DOSEoral.A every 24 hours for 1 total doses
    Lex.oral <- ev (ID   = 1,            ## One individual
                    amt  = LDOSEoral,    ## Amount of dose 
                    ii   = tinterval,    ## Time interval
                    addl = LTDOSE - 1,   ## Addtional doseing 
                    cmt  = "AST",        ## The dosing comaprtment: AST Stomach  
                    replicate = FALSE)   ## No replicate
    
    Ltsamp       = tgrid(0, tinterval*(LTDOSE - 1) + 24*1, 1) ## Simulation time from PND0 to PND20 plus one day without dosing
    
    
    Lout_A3 <- Lmod_R %>% 
               init(APlas_free = Ginit_A3$APlas_free, APTC = Ginit_A3$APTC, AFil = Ginit_A3$AFil, AKb = Ginit_A3$AKb, ARest = Ginit_A3$ARest,
               AL = Ginit_A3$AL, AM = Ginit_A3$AM, AF = Ginit_A3$AF, A_baso = Ginit_A3$A_baso, A_apical = Ginit_A3$A_apical, Adif = Ginit_A3$Adif,
               Aefflux = Ginit_A3$Aefflux, APlas_free_pup = Ginit_A3$APlas_Fet) %>%
               param (Lpars) %>%
               update(atol = 1E-3, maxsteps = 500000) %>%          
               mrgsim_d (data = Lex.oral, tgrid = Ltsamp)
    
    Lout_A4 <- Lmod_R %>% 
               init(APlas_free = Ginit_A4$APlas_free, APTC = Ginit_A4$APTC, AFil = Ginit_A4$AFil, AKb = Ginit_A4$AKb, ARest = Ginit_A4$ARest,
               AL = Ginit_A4$AL, AM = Ginit_A4$AM, AF = Ginit_A4$AF, A_baso = Ginit_A4$A_baso, A_apical = Ginit_A4$A_apical, Adif = Ginit_A4$Adif,
               Aefflux = Ginit_A4$Aefflux, APlas_free_pup = Ginit_A4$APlas_Fet) %>%
               param (Lpars) %>%
               update(atol = 1E-3, maxsteps = 500000) %>%          
               mrgsim_d (data = Lex.oral, tgrid = Ltsamp)
    
    
    Loutdf_A3 <- as.data.frame(Lout_A3) %>% select (Time = time, CPlas = Plasma, AUC_CPlas = AUC_CPlas)
    Loutdf_A4 <- as.data.frame(Lout_A4) %>% select (Time = time, CPlas = Plasma, AUC_CPlas = AUC_CPlas)
    Loutdf_A3$Time <- Loutdf_A3$Time + (24*20)
    Loutdf_A4$Time <- Loutdf_A4$Time + (24*20)
    
    return (list("A1" = Goutdf_A1, "A2" = Goutdf_A2, "A3" = Loutdf_A3, "A4" = Loutdf_A4))
    
}


## Define human model
pred.human <- function(Gpars_H, Lpars_H, DOSE) {
    
    ## Exposure scenario for Lactational exposure; through GD(-53) - GD21 (end of gestation)
    ## Defined the exposure scenario for age specific data
    ex <- tibble(ID   = rep(1, 365*30 + 1), # individual ID 
                 time = seq(from = 0, to = 24*365*30, by = 24)) %>% # time from 0 to 30 years
        mutate (DAY   = time/24, YEAR  = DAY/365, 
        BW    = if_else(YEAR <= 18, # if age small than or equal to 18 years old use the equation; otherwise bodyweight equal to about 54 kg
                                true  = (-2.561*YEAR^4 + 85.576*YEAR^3 - 855.95*YEAR^2 + 5360.6*YEAR + 4428.5)/1000,
                                ifelse(YEAR >= 30, 67, 54)))
    
    tsamp <- tgrid (start = 0, end = 365*30, delta = 0.1) # simulation time from 0 to 30 years old, and the time interval is 0.1
    
    ## Exposure scenarior:  
    # ## Exposure scenarior: Daily dose to 4.5 ng/kg/day for 0-25 years (1976 - 2001); daily dose to 4.5*0.34 ng/kg/day for 6 years (2001 - 2007) matrix: plasma (mg/L)
    PDOSEoral_1 = DOSE #0.0000045  ## mg/kg-d, daily oral dose before 2000
    ex_1 <- mutate (ex, amt = case_when (YEAR < 20 ~ PDOSEoral_1*BW,
                                         YEAR >= 20 ~ PDOSEoral_1*BW*1), # adj.factor: default is 0.34
                    cmt  = "AST", ii = 24, evid = 1, time = DAY)
    
    
    
    out <- PreGmod_H %>%
           update(atol = 1E-8, maxsteps = 500000) %>%          
           mrgsim_d(data = ex_1, tgrid = tsamp)%>%
           filter (time > 0)
    
    PreG_Init <- out %>% filter (row_number()== n()) %>% select(-c("Plasma", "Liver", "Kidney"))
    
    ############## Gestatonal model
    ## Get out of log domain
    Gpars <- exp(Gpars_H)                 ## Return a list of exp (parametrs for gestational model) from log scale
    
    ## Exposure scenario for gestational exposure
    GBW          = 67                     ## Body weight before gestation (measrument data if available); 
    tinterval    = 24                     ## Time interval; 
    GTDOSE       = 7*40                   ## Total dosing/Dose times; Repeat oral dose from GA40 (Weeks)
    GDOSE        = DOSE                   ## Input oral dose  
    GDOSEoral    = GDOSE*GBW              ## Amount of oral dose
    
    # To create a data set of 1 subject receiving DOSEoralevery 24 hours 
    Gex.oral <- ev (ID   = 1,             ## One individual
                    time = 0,             ## Dossed strat time (GA0)
                    amt  = GDOSEoral,     ## Amount of dose 
                    ii   = tinterval,     ## Time interval
                    addl = GTDOSE - 1,    ## Addtional doseing 
                    cmt  = "AST",         ## The dosing comaprtment: AST Stomach  
                    replicate = FALSE)    ## No replicate
    
    Gtsamp_A1  = tgrid(0, tinterval*(GTDOSE - 1) + 24*7, 1) ## Simulation time from GA0 to GA 40 
    Gtsamp_A2  = tgrid(0, tinterval*(GTDOSE - 1) + 24*7, 1) ## Simulation time from GA0 to GA 40 

    ## Simulation of exposure scenaior A 
    
    
    Gout_A1 <- Gmod_H %>% init(APlas_free = PreG_Init$APlas_free, APTC = PreG_Init$APTC, AFil = PreG_Init$AFil, AKb = PreG_Init$AKb, ARest = PreG_Init$ARest,
                               AL = PreG_Init$AL, AM = PreG_Init$AM, AF = PreG_Init$AF, A_baso = PreG_Init$A_baso, A_apical = PreG_Init$A_apical, Adif = PreG_Init$Adif,
                               Aefflux = PreG_Init$Aefflux) %>%
                               param (Gpars) %>% update(atol = 1E-3, maxsteps = 500000) %>%          
                               mrgsim_d (data = Gex.oral, tgrid = Gtsamp_A2)
    
    Gout_A2 <- Gmod_H %>% init(APlas_free = PreG_Init$APlas_free, APTC = PreG_Init$APTC, AFil = PreG_Init$AFil, AKb = PreG_Init$AKb, ARest = PreG_Init$ARest,
                               AL = PreG_Init$AL, AM = PreG_Init$AM, AF = PreG_Init$AF, A_baso = PreG_Init$A_baso, A_apical = PreG_Init$A_apical, Adif = PreG_Init$Adif,
                               Aefflux = PreG_Init$Aefflux) %>%
                               param (Gpars) %>% update(atol = 1E-3, maxsteps = 500000) %>%          
                               mrgsim_d (data = Gex.oral, tgrid = Gtsamp_A2)
    
    
    Goutdf_A1 <- as.data.frame(Gout_A1) %>% select (Time = time, CPlas = Plasma, AUC_CPlas = AUC_CPlas)
    Ginit_A2  <- as.data.frame(Gout_A2) %>% filter (row_number()== n()) 

    ############### Lactational model ##############################
    Lpars <- exp(Lpars_H)          ## Return a list of exp (parametrs for gestational model) from log scale
    
    ## Exposure scenario for Lactational exposure; 
    LBW          = 67                    ## body weight 
    tinterval    = 24                    ## Time interval; 
    LTDOSE       = 7*41                  ## Total dosing/Dose times; 
    LDOSE        = DOSE                  ## Repeat oral dose of GDOSE mg/kg/day;  
    LDOSEoral    = LDOSE*LBW             ## Amount of oral dose
    
    
    # To create a data set of 1 subject receiving Dose every 24 hours 
    Lex.oral <- ev (ID   = 1,            ## One individual
                    amt  = LDOSEoral,    ## Amount of dose 
                    ii   = tinterval,    ## Time interval
                    addl = LTDOSE - 1,   ## Addtional doseing 
                    cmt  = "AST",        ## The dosing comaprtment: AST Stomach  
                    replicate = FALSE)   ## No replicate
    
    Ltsamp       = tgrid(0, tinterval*(LTDOSE - 1) + 24*7, 1) ## Simulation time 
    
    
    Lout_A2 <- Lmod_H %>% 
               init(APlas_free = Ginit_A2$APlas_free, APTC = Ginit_A2$APTC, AFil = Ginit_A2$AFil, AKb = Ginit_A2$AKb, ARest = Ginit_A2$ARest,
               AL = Ginit_A2$AL, AM = Ginit_A2$AM, AF = Ginit_A2$AF, A_baso = Ginit_A2$A_baso, A_apical = Ginit_A2$A_apical, Adif = Ginit_A2$Adif,
               Aefflux = Ginit_A2$Aefflux, APlas_free_neo = Ginit_A2$APlas_Fet) %>%
               param (Lpars) %>%
               update(atol = 1E-3, maxsteps = 500000) %>%          
               mrgsim_d (data = Lex.oral, tgrid = Ltsamp)
    
    
    
    
    Loutdf_A2 <- as.data.frame(Lout_A2) %>% select (Time = time, CPlas = Plasma, AUC_CPlas = AUC_CPlas)
    Loutdf_A2$Time <- Loutdf_A2$Time + (24*7*40)

    return (list("G" = Goutdf_A1, "L" = Loutdf_A2))
}

```

# Monte Carlo simulation
In the Monte Carlo simulation, the sensitive parameters were chosen by sensitivity analiysis and then were assigned as probabilistic distributions (please refer to Tables S8-S9). 

```{r}

# Create the list object
HED_A1_A <- list()
HED_A2_A <- list()
HED_A3_A <- list()
HED_A4_A <- list()
HED_A1_B <- list()
HED_A2_B <- list()
HED_A3_B <- list()
HED_A4_B <- list()
ASC_A1   <- list()
ASC_A2   <- list()
ASC_A3   <- list()
ASC_A4   <- list()

## Monte Carlo simulation
N = 10 # For testing purpose, we use 10 iterations. 
## Use N = 1000 to reproduce results in Table 5. The results using 10 vs. 1000 are similar.

for (i in 1:N){
#Defined the parameters with Monte carlo analysis (please refer to Tables S8-S9).
    Gpars_R  <- log(c(
        BW        = rnormTrunc (1, min = 0.15, max = 0.57, mean = 0.36, sd = 0.108),
        VLC       = rnormTrunc  (1, min = 0.01, max = 0.06, mean = 0.04, sd = 0.01),
        KbileC    = rlnormTrunc (1, min = exp(-5.38), max = exp(-4.63), meanlog = -5.00, sdlog = 0.19),
        PL        = rlnormTrunc (1, min = exp(0.88), max = exp(1.39), meanlog = 1.13, sdlog = 0.13),
        PRest     = rlnormTrunc (1, min = exp(-1.79), max = exp(-1.28), meanlog = -1.53, sdlog = 0.13),
        Ktrans1C  = rlnormTrunc (1, min = exp(-0.18), max = exp(0.58), meanlog = 0.20, sdlog = 0.19),
        Ktrans2C  = rlnormTrunc (1, min = exp(-0.42), max = exp(0.34), meanlog = -0.04, sdlog = 0.19),
        Ktrans3C  = 0.23,
        Free      = 0.019,
        Vmax_baso_invitro = 221,
        Km_baso   = 19.9,
        Free_Fet  = 0.022,
        PL_Fet    = 2.55
    ))    
    
    Lpars_R  <- log(c(
        Free        = rlnormTrunc (1, min = exp(-6.01), max = exp(-5.32), meanlog = -5.62, sdlog = 0.198),
        Free_pup    = rlnormTrunc (1, min = exp(-4.22), max = exp(-3.44), meanlog = -3.84, sdlog = 0.198),
        GFRC        = rnormTrunc  (1, min = 24.95, max = 57.13, mean = 41, sd = 8.208),
        KbileC      = rlnormTrunc (1, min = exp(-6.57), max = exp(-5.41), meanlog = -5.99, sdlog = 0.294),
        Km_apical_p = rlnormTrunc (1, min = exp(5.009), max = exp(6.16), meanlog = 5.58, sdlog = 0.29),
        KMilk0      = rlnormTrunc (1, min = exp(-1.68), max = exp(-0.90), meanlog = -1.29, sdlog = 0.13), 
        KurineC_pup = rlnormTrunc (1, min = exp(-0.148), max = exp(1.002), meanlog = 0.45, sdlog = 0.19),
        PL          = rlnormTrunc (1, min = exp(0.59), max = exp(1.37), meanlog = 0.98, sdlog = 0.198),
        PL_pup      = rlnormTrunc (1, min = exp(0.53), max = exp(1.30), meanlog = 0.92, sdlog = 0.198),
        PMilkM      = rlnormTrunc (1, min = exp(0.22), max = exp(1.17), meanlog = 0.60, sdlog = 0.19),
        PRest_pup   = rlnormTrunc (1, min = exp(-1.92), max = exp(-1.14), meanlog = -1.53, sdlog = 0.13),
        RAFapi      = rlnormTrunc (1, min = exp(0.80), max = exp(1.955), meanlog = 1.38, sdlog = 0.29),
        VFilC       = rnormTrunc  (1, min = 0.00035, max = 0.00133, mean = 0.00084, sd = 0.00025),
        Vmax_apical_invitro_p = rlnormTrunc (1, min = exp(5.35), max = exp(6.507), meanlog = 5.93, sdlog = 0.29),
        Vmax_apical_invitro = 4141,
        PRest       = 0.03,
        SA_BW       = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_VLC      = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_KMilkC   = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_VL_pup   = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2)
    ))
    
    Gpars_H  <- log(c(
        BW        = rnormTrunc (1, min = 27.89, max = 107.5, mean = 67.7, sd = 20.3),
        SA_Htc    = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_QC     = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_QK_P   = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        Free      = rlnormTrunc (1, min = exp(-6.53), max = exp(-5.38), meanlog = -5.96, sdlog = 0.29),  
        Free_Fet  = rlnormTrunc (1, min = exp(-6.19), max = exp(-5.04), meanlog = -5.61, sdlog = 0.29),
        KeffluxC  = rlnormTrunc (1, min = exp(-4.82), max = exp(-3.67), meanlog = -4.24, sdlog = 0.29), 
        Ktrans1C  = rlnormTrunc (1, min = exp(-0.85), max = exp(0.29), meanlog = -0.28, sdlog = 0.29), 
        Ktrans2C  = rlnormTrunc (1, min = exp(-0.51), max = exp(0.65), meanlog = 0.07, sdlog = 0.29), 
        QCC       = rnormTrunc  (1, min = 6.76, max = 26.04, mean = 16.4, sd = 4.92), 
        Km_apical = 248,
        PPla      = 0.13,
        PL_Fet    = 0.58,
        PRest_Fet = 2.3
    ))    
    
    Lpars_H <- log(c(
        SA_BW     = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        SA_BW_neo = rnormTrunc (1, min = 0.61, max = 1.39, mean = 1, sd = 0.2),
        Free      = rlnormTrunc (1, min = exp(-3.68), max = exp(-2.94), meanlog = -3.32, sdlog = 0.07), 
        Free_neo  = rlnormTrunc (1, min = exp(-4.71), max = exp(-3.87), meanlog = -4.29, sdlog = 0.13),
        KeffluxC  = rlnormTrunc (1, min = exp(-2.52), max = exp(-1.36), meanlog = -1.94, sdlog = 0.19),
        KeffluxC_neo = rlnormTrunc (1, min = exp(-2.52), max = exp(-1.36), meanlog = -1.94, sdlog = 0.19),
        PAMilkC    = rlnormTrunc (1, min = exp(-6.49), max = exp(-5.35), meanlog = -3.6, sdlog = 0.29),
        PRest     = rlnormTrunc (1, min = exp(-2.02), max = exp(-1.24), meanlog = -1.63, sdlog = 0.13),
        PRest_neo = rlnormTrunc (1, min = exp(-2.02), max = exp(-1.24), meanlog = -1.63, sdlog = 0.13),
        QCC       = rnormTrunc (1, min = 6.76, max = 26.04, mean = 16.4, sd = 3.28),
        QKC       = rnormTrunc (1, min = 0.07, max = 0.28, mean = 0.175, sd = 0.035),
        RAFbaso   = rlnormTrunc (1, min = exp(-0.618), max = exp(-0.532), meanlog = -0.043, sdlog = 0.29),
        VKC       = rnormTrunc (1, min = 0.002, max = 0.01, mean = 0.004, sd = 0.001),
        RAFapi   = 0.525
    ))    
    
    

outdf_A1_R  <- pred.rat(Gpars_R, Lpars_R, 1)[[1]]   %>% filter (Time == 20*24) %>% select(AUC_CPlas)
    outdf_A2_R  <- pred.rat(Gpars_R, Lpars_R, 0.4)[[2]] %>% filter (Time == 20*24) %>% select(AUC_CPlas)
    outdf_A3_R  <- pred.rat(Gpars_R, Lpars_R, 0.1)[[3]] %>% filter (Time == 40*24) %>% select(AUC_CPlas)
    outdf_A4_R  <- pred.rat(Gpars_R, Lpars_R, 0.3)[[4]] %>% filter (Time == 40*24) %>% select(AUC_CPlas)
    
    outdf_A1_H  <- pred.human(Gpars_H, Lpars_H, 1)[[1]]   %>% filter (Time == 40*24*7) %>% select(AUC_CPlas)
    outdf_A2_H  <- pred.human(Gpars_H, Lpars_H, 0.4)[[1]] %>% filter (Time == 40*24*7) %>% select(AUC_CPlas)
    outdf_A3_H  <- pred.human(Gpars_H, Lpars_H, 0.1)[[2]] %>% filter (Time == 70*24*7) %>% select(AUC_CPlas)
    outdf_A4_H  <- pred.human(Gpars_H, Lpars_H, 0.3)[[2]] %>% filter (Time == 70*24*7) %>% select(AUC_CPlas)
    
###########
## Define the Monte Carlo simulation function for rats to estimate the probablistic AUC based on NOAEL
    
    ASC_A1 [[i]]   <- outdf_A1_R/(20*24) # A1 Lau et al. 2003       : (GD2 - GD21)   : NOAEL = 1.0 mg/kg-day
    ASC_A2 [[i]]   <- outdf_A2_R/(78*24) # A2 Luebker et al. 2005b  : (PREG - G20)   : NOAEL = 0.4 mg/kg-day
    ASC_A3 [[i]]   <- outdf_A3_R/(98*24) # A3 Luebker et al. 2005a  : (PREG - PND20) : NOAEL = 0.1 mg/kg-day
    ASC_A4 [[i]]   <- outdf_A4_R/(41*24) # A4 Butenhoff et al. 2009 : (GD0 - PND20)  : NOAEL = 0.3 mg/kg-day
    
## The calculation of HED based on EPA method (method 1)
    HED_A1_A [[i]]   <- ((ASC_A1[[i]])*0.000081) 
    HED_A2_A [[i]]   <- ((ASC_A2[[i]])*0.000081) 
    HED_A3_A [[i]]   <- ((ASC_A3[[i]])*0.000081) 
    HED_A4_A [[i]]   <- ((ASC_A4[[i]])*0.000081) 
    
## The calculation of HED  based on AUC method (method 2: traditional PBPK method)
    HED_A1_B [[i]]   <- 1*  ((outdf_A1_R) / (outdf_A1_H )) 
    HED_A2_B [[i]]   <- 0.4*((outdf_A2_R) / (outdf_A2_H )) 
    HED_A3_B [[i]]   <- 0.1*((outdf_A3_R) / (outdf_A3_H )) 
    HED_A4_B [[i]]   <- 0.3*((outdf_A4_R) / (outdf_A4_H )) 
    

}

```

# Estimate the median (95% CI) of ASC (mg/L) and HED (mg/kg/day)

```{r}
Range_ASC_A1 <- do.call (rbind, ASC_A1)%>%
        summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95  = quantile (AUC_CPlas , probs = 0.975),
        ci_05  = quantile (AUC_CPlas , probs = 0.025))

Range_ASC_A2 <- do.call (rbind, ASC_A2)%>%  
        summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95  = quantile (AUC_CPlas , probs = 0.975),
        ci_05  = quantile (AUC_CPlas , probs = 0.025))

Range_ASC_A3 <- do.call (rbind, ASC_A3)%>% 
        summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95  = quantile (AUC_CPlas , probs = 0.975),
        ci_05  = quantile (AUC_CPlas , probs = 0.025))

Range_ASC_A4 <- do.call (rbind, ASC_A4)%>%  
        summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95  = quantile (AUC_CPlas , probs = 0.975),
        ci_05  = quantile (AUC_CPlas , probs = 0.025))



## Method 1:ASC 
Range_HED_A1_A <- do.call (rbind, HED_A1_A)%>%  
        summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95 = quantile (AUC_CPlas , probs = 0.975),
        ci_05 = quantile (AUC_CPlas , probs = 0.025))

Range_HED_A2_A <- do.call (rbind, HED_A2_A)%>%  
        summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95 = quantile (AUC_CPlas , probs = 0.975),
        ci_05 = quantile (AUC_CPlas , probs = 0.025))

Range_HED_A3_A <- do.call (rbind, HED_A3_A)%>%   
    summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95 = quantile (AUC_CPlas , probs = 0.975),
        ci_05 = quantile (AUC_CPlas , probs = 0.025))

Range_HED_A4_A <- do.call (rbind, HED_A4_A)%>%  
    summarize (
        median = quantile (AUC_CPlas , probs = 0.5), 
        ci_95 = quantile (AUC_CPlas , probs = 0.975),
        ci_05 = quantile (AUC_CPlas , probs = 0.025))


### Method 2:AUC ratios

Range_HED_A1_B <- do.call (rbind, HED_A1_B)%>%  
                summarize (
                median = quantile (AUC_CPlas , probs = 0.5), 
                ci_95 = quantile (AUC_CPlas , probs = 0.975),
                ci_05 = quantile (AUC_CPlas , probs = 0.025))

Range_HED_A2_B <- do.call (rbind, HED_A2_B)%>%  
                summarize (
                median = quantile (AUC_CPlas , probs = 0.5), 
                ci_95 = quantile (AUC_CPlas , probs = 0.975),
                ci_05 = quantile (AUC_CPlas , probs = 0.025))

Range_HED_A3_B <- do.call (rbind, HED_A3_B)%>%  
                summarize (
                median = quantile (AUC_CPlas , probs = 0.5), 
                ci_95 = quantile (AUC_CPlas , probs = 0.975),
                ci_05 = quantile (AUC_CPlas , probs = 0.025))

Range_HED_A4_B <- do.call (rbind, HED_A4_B)%>%  
                summarize (
                median = quantile (AUC_CPlas , probs = 0.5), 
                ci_95 = quantile (AUC_CPlas , probs = 0.975),
                ci_05 = quantile (AUC_CPlas , probs = 0.025))


```
# Show the predicted values
Here, we make a table to display the predicted average serum concentration (ASC, mg/L) and HED (ug/kg/day) based on the selected studies:

- A1: Lau et al. 2003: (GD2- GD21): NOAEL = 1.0 mg/kg-day
- A2: Luebker et al. 2005b  : (PREG - G20)   : NOAEL = 0.4 mg/kg-day
- A3: Luebker et al. 2005a  : (PREG - PND20) : NOAEL = 0.1 mg/kg-day
- A4: Butenhoff et al. 2009 : (GD0 - PND20)  : NOAEL = 0.3 mg/kg-day


```{r}
## Make a ASC table
ASC <- rbind.data.frame(
       A1 = Range_ASC_A1*1000,
       A2 = Range_ASC_A2*1000,
       A3 = Range_ASC_A3*1000,
       A4 = Range_ASC_A4*1000
)

ASC
## Make a HED table (method 1)
HED_A<- rbind.data.frame(
       A1 = Range_HED_A1_A*1000,
       A2 = Range_HED_A2_A*1000,
       A3 = Range_HED_A3_A*1000,
       A4 = Range_HED_A4_A*1000
)

HED_A
## Make a HED table (method 2)
HED_B<- rbind.data.frame(
       A1 = Range_HED_A1_B*1000,
       A2 = Range_HED_A2_B*1000,
       A3 = Range_HED_A3_B*1000,
       A4 = Range_HED_A4_B*1000
)
HED_B

```






